GMU MS SWE Handbook\\{\large A Handbook For the Masters of Software Engineering program at George Mason University

### 2024-10-26 ennv.tex
updates

\paragraph{Convolutional Neural Networks (CNNs)} are a type of neural network that is often used in image recognition and classification.  CNNs consist of of neurons that have learnable weights and biases. Each neuron receives several inputs, takes a weighted sum over them, passes it through an activation function, and responds with an output.

\paragraph{Recurrent Neural Networks} Recurrent Neural Networks (RNNs) are a type of neural network that is often used in natural language processing and speech recognition. RNNs are designed to recognize patterns in sequences of data. RNNs have loops in them, allowing information to persist. This loop allows information to be passed from one step of the network to the next.

>>>>

\paragraph{Convolutional Neural Networks (CNNs)} CNNs, often used in image recognition and classification, consist of neurons that have learnable weights and biases. Each neuron receives several inputs, takes a weighted sum over them, passes it through an activation function, and responds with an output.

\paragraph{Recurrent Neural Networks (RNNs)} RNNs, often used in natural language process and speech recognition, are designed to recognize patterns in sequences of data. RNNs have \emph{loops} in them, allowing information to be sent forward and backward.
